---
title: "Getting Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{getting-started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(textclassificationexamples)
library(ggplot2)
library(rpart)
```

This package is intended to provide users with datasets and helper functions necessary to work through basic text classification and modeling examples.

# Spam

The Spam example lets students work with email subject lines from a model eliciting activity that was created by Joan Garfield and colleagues at the University of Minnesota (see https://serc.carleton.edu/sp/library/mea/index.html).

# Clickbait 
The clickbait example lets students work through a different classification problem using headlines from sites known to host clickbait and legitimate news sites.

The intent is to extract a variety of structural features from headlines associated with either valid news sources or clickbait articles to create a model/ classification scheme that accurately classifies headlines based on the *clickbait* variable (TRUE/FALSE).

There are three available datasets for use: **articles**, **articles_clean**, and **sample_articles**. 

**articles** contains the entire dataset provided by the source (see documentation for more info). **articles_clean** is a marginally smaller subset of **articles** filtered (imperfectly) for headlines with explicit language, with **sample_articles** being a 2000 row sample of this subset. **sample_articles** contains 1000 rows of clickbait articles, and 1000 rows of news headlines. This small set can be converted to a testing and training set for modeling purposes.

```{r}
head(sample_articles)
```

